Discon analysis

### 2018-08-08 analysis/01_analysis.Rmd
new categories: instruments, buildings. New novel items
shuffle trial sets

```{r plot1}
plot1 <- data %>%
  filter(phase == 'test') %>%
  group_by(distribution, workerid) %>%
  summarise(correct = mean(correct_target1),
            correct2 = mean(correct_target2),
            correct3 = mean(correct_target3)) %>%
  gather(item, prop_correct, -distribution, -workerid) %>%
  group_by(distribution, item) %>%
  multi_boot_standard(col = "prop_correct")

ggplot(plot1,
       aes(x = item, y=mean, fill=item)) +
  geom_bar(stat='identity') +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  facet_grid(~distribution) +
  geom_hline(yintercept = 1/3, lty=2) +
  ylim(0, 1) +
  theme_few()

@@

```{r plot 2}
plot2 <- data %>%
  filter(phase == 'test') %>%
  group_by(distribution, workerid, trialType) %>%
  summarise(correct = mean(correct_target1),
            correct2 = mean(correct_target2),
            correct3 = mean(correct_target3)) %>%
  gather(item, prop_correct, -distribution, -workerid, -trialType) %>%
  group_by(distribution, trialType, item) %>%
  multi_boot_standard(col = "prop_correct")

@@

>>>>

```{r plot1}
plot1 <- data %>%
  filter(phase == 'test') %>%
  group_by(distribution, target1, workerid) %>%
  summarise(correct = mean(correct_target1),
            correct2 = mean(correct_target2),
            correct3 = mean(correct_target3)) %>%
  gather(item, prop_correct, -distribution, -workerid, -target1) %>%
  group_by(distribution, target1, item) %>%
  multi_boot_standard(col = "prop_correct")

ggplot(plot1,
       aes(x = item, y=mean, fill=item)) +
  geom_bar(stat='identity') +
#  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  facet_grid(target1~distribution) +
  geom_hline(yintercept = 1/3, lty=2) +
  ylim(0, 1) +
  theme_few()

@@

```{r plot 2}
plot2 <- data %>%
  filter(phase == 'test') %>%
  group_by(distribution, workerid, trialType) %>%
  summarise(correct = mean(correct_target1),
            correct2 = mean(correct_target2),
            correct3 = mean(correct_target3)) %>%
  gather(item, prop_correct, -distribution, -workerid, -trialType) %>%
  arrange(workerid)

 # group_by(distribution, trialType, item) %>%
 # multi_boot_standard(col = "prop_correct")

ggplot() + 
  geom_jitter(data = plot2, 
              aes(x = item, y=prop_correct, fill=item, col=trialType),
              height = 0.1,
              width = 0.1) +
  facet_grid(trialType~distribution) +
  theme(legend.position="none")

plot2 <- data %>%
  filter(phase == 'test') %>%
  group_by(distribution, workerid, trialType) %>%
  summarise(correct = mean(correct_target1),
            correct2 = mean(correct_target2),
            correct3 = mean(correct_target3)) %>%
  gather(item, prop_correct, -distribution, -workerid, -trialType) %>%
  group_by(distribution, trialType, item) %>% 
  multi_boot_standard(col = "prop_correct")

@@

```{r}
data %>%
  filter(phase == "test", distribution == "c(6, 0, 0)") %>%
  group_by(pick) %>%
  summarise(n = length(correct_target1),
            mean = mean(correct_target1)) %>%
  arrange(mean)
```
